### 2021-04-20 input/background.tex
small fixes in background and related work

Numerous studies exist on content indexing, either being centralized or distributed (see Section\ref{related_work}). In this paper
we advocate solutions that do not rely on requesting any remote entity before being able to access a given content. 
Indeed, in the Fog context, requesting a remote node before accessing any content has many drawbacks as previsoulsy explained.
This section thus focus on the existing solutions so that: \textbf{for any content, every node is able to access its closest replica without any prior request.}
We explain why existing implementations are costly thus preventing their deployment in real systems.
Then, we describe the problem tackled by this paper at an abstract level to underline the challenges that drove the design of our proposal.

\subsection*{Disseminate localization information}
Enabling the accessibility of content without prior requests implies that the information about replica localization has to be pushed directly to the nodes.
Broadcasting information about cache updates to all nodes in the system is a straightforward way to maintain consistent information about replica localization for all nodes~\cite{nlsr,lscr}. Indeed, having the entire knowledge of all the replica localizations along with distance information carried into messages, each node can easily compute where the closest copy of a given object resides, without contacting any remote node. Moreover, removing the lookup latency directly involves faster downloading times. 
Similarly, one could solve this issue by using a conflict-free replicated datantype (CRDT) for set data structures, for example~\cite{shapiro2011crdts}. 
However, either by broadcasting or with CRDTs, both inherently imply that every nodes will eventually receive all messages. 
That means information that might only interests a small subset of nodes is actually spread out all over the network.

\subsection*{Locking down the dissemination}
To provide the intuition underlying our proposal, we now describe the problem tackled by this paper at an abstract level. 
Suppose there exists an oracle in the system that instantly knows the arrival/departure of nodes in the topology, and the location of the creation/removal of replicas. In other words, this oracle is constantly aware of the current topology and the current list of all available replicas of a given content in the system. Equipped with these two information, it is then trivial for this oracle to compute for each node, where resides its closest replica for a given content. Mapping each node of the topology to a single replica amounts to partition the set of all nodes into $k$ disjoint sets (or partitions), where $k$ is the number of current replicas. Thus, every node in the same partition would get the content from the same replica. Interestingly, this partitioning matches the physical topology as neighbors physically closed in the infrastructure will most likely reside in the same partition.
For any event such as an arrival/departure of nodes or creation/removal of replicas, the oracle is thus able to inform the \textit{exact} subset of nodes that has to update their location (\ie the exact scope of an event). 
The challenge of implementing such a partitioning in an asynchronous network resides in informing this same subset of nodes (or as close as possible), without any \textit{a priori} knowledge while only relying on local information (\ie no node has the knowledge of all the replica localizations).

Finally, we emphasize that information about a given replica localization should remain in a given geographical scope. 
Intuitively, it is most likely that events happening at a given place in the network will have no impact on nodes that are very far away from them.
This prevents the use of gossip protocols for example.  Indeed, gossip protocols are also appealing candidates to disseminate information reliably across a network~\cite{epidemic-protocol} and numerous studies have shown how quickly they converge despite high level of churn and/or failures~\cite{lpbcast}.
However, these protocols usually relies on a so-called \textit{peer-sampling service}~\cite{jelasity2007gossip} to efficiently propagate the information. This implies that nodes will exchange messages with random nodes in the system far exceeding the geograhical scope.

>>>>

Numerous studies exist on content indexing, with solutions being either centralized or distributed (see Section\ref{related_work}). As explained above, in this paper we advocate designs that do not rely on requesting any remote entity before being able to access a given content.
This section thus focuses on the existing solutions so that: \textbf{for any content, every node is able to access its closest replica without any prior request.}
We explain why existing implementations are costly thus preventing their deployment in real systems.
Then, we describe the problem tackled by this paper at an abstract level to underline the challenges that drove the design of our proposal.

\subsection*{Disseminate localization information}
Enabling the accessibility of content without prior requests implies that the information about replica localization has to be pushed directly to the nodes.
Broadcasting information about cache updates to all nodes in the system is a straightforward way to maintain consistent information about replica localization for all nodes~\cite{nlsr,lscr}. Indeed, having the entire knowledge of all the replica localizations along with distance information carried into messages, each node can easily compute where the closest copy of a given object resides, without contacting any remote node. Moreover, removing the lookup latency directly involves faster downloading times. 
Similarly, one could solve this issue by using a conflict-free replicated datatype (CRDT) for set data structures, for example~\cite{shapiro2011crdts}. 
However, either by broadcasting or with CRDTs, both inherently imply that every nodes will eventually receive all messages. 
That means information that might only interests a small subset of nodes is actually spread out all over the network.

\subsection*{Locking down the dissemination}
To provide the intuition underlying our proposal, we now describe the problem tackled by this paper at an abstract level, and explain how an (imaginary) omniscient entity could solve it. 
In this way, suppose there exists an \textit{oracle} in the system that instantly knows the arrival/departure of nodes in the topology, and the location of the creation/removal of replicas. In other words, this oracle is constantly aware of the current topology and the current list of all available replicas of a given content in the system. Equipped with these two information, it is then trivial for this oracle to compute for each node, where resides its closest replica for a given content. Mapping each node of the topology to a single replica amounts to partition the set of all nodes into $k$ disjoint sets (or partitions), where $k$ is the number of current replicas. Thus, every node in the same partition would get the content from the same replica. Interestingly, this partitioning matches the physical topology as neighbors physically closed in the infrastructure will most likely reside in the same partition.
For any event such as an arrival/departure of nodes or creation/removal of replicas, the oracle is thus able to inform the \textit{exact} subset of nodes that has to update their location (\ie the exact scope of an event). 
The challenge of implementing such a partitioning in an asynchronous network resides in informing this same subset of nodes (or as close as possible), without any \textit{a priori} knowledge while only relying on local information (\ie no node has the knowledge of all the replica localizations).

Moreover, we emphasize that information about a given replica localization should remain in a given geographical scope. 
Intuitively, it is most likely that events happening at a given place in the network will have no impact on nodes that are very far away from them.
This prevents the use of gossip protocols for example.  Indeed, gossip protocols are also appealing candidates to disseminate information reliably across a network~\cite{epidemic-protocol} and numerous studies have shown how quickly they converge despite high level of churn and/or failures~\cite{lpbcast}.
However, these protocols usually relies on a so-called \textit{peer-sampling service}~\cite{jelasity2007gossip} to efficiently propagate the information. This implies that nodes will exchange messages with random nodes in the system far exceeding their geograhical scope.

### 2021-04-20 input/related_work.tex
small fixes in background and related work

In the context of this paper, an \textit{ideal} content indexing service would enable that for any content, every node would be able to access its closest replica.
Basically, offering such a service would require (i) to have access to the list, namely the \textit{index}, of current replica localizations, (ii) to be aware of the topology to compute which replica is the closest for a given location. We review the existing solutions

(i) Deploying a centralized server that maintain an index of all replica localizations has been proposed~\cite{fogstore, p2p-alto, p2p-oracle, snamp}. However, this solution suffers from well-known disadvantages inherent to centralized solutions (load balancing, robustness, locality, etc.) that are even magnified in a Fog context.
Distributing this index among nodes in the network circumvent some of these issues, either using coordinate-based overlays~\cite{coin_19, voronet} or Distributed Hash Tables~\cite{squirrel, ipfs, dht-name-resolution, mdht} for example. In the latter, each node stores a part of the index, defined by an interval between hash values. 
Before downloading any object, a node first
hashes the content to obtain the address of the node that stores the replica localizations of this given object. After obtaining from the remote node the list of available replicas, it can select the closest copy to download from. We emphasize that, in this setting, the DHT only stores information about replicas localizations, not the content itself. DHT-based approaches are well-studied and easy to deploy in order to offer such a localization service.

>>>>

In the context of this paper, a content indexing service enables that for any content, every node is able to access its closest replica.
Basically, offering such a service requires (i) to have access to the list of current replica localizations, (ii) to be aware of the topology to compute which replica is the closest for a given location.

(i) Deploying a centralized server that maintain an index of all replica localizations has been proposed~\cite{fogstore, p2p-alto, p2p-oracle, snamp}. However, this solution suffers from well-known disadvantages inherent to centralized solutions (load balancing, robustness, locality, etc.) that are even magnified in an Edge context.
Distributing this index among nodes in the network circumvent some of these issues, either using coordinate-based overlays~\cite{coin_19, voronet} or Distributed Hash Tables~\cite{squirrel, ipfs, dht-name-resolution, mdht} for example. In the latter, each node stores a part of the index, defined by an interval between hash values. 
Before downloading any object, a node first
hashes the content to obtain the address of the node that stores the replica localizations of this given object. After obtaining from the remote node the list of available replicas, it can select the closest copy to download from. We emphasize that, in this setting, the DHT only stores information about replicas localizations, not the content itself. DHT-based approaches are well-studied and easy to deploy in order to offer such a localization service.
